---
title: "Backend development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(carpentr)
library(tidyverse)
```

## Read in EITI production data

The function `read_eiti()` reads in EIT production data from the API for a given country and year.

```{r read_eiti_production}

sn17 <- read_eiti("SN",2017,'production')
sn17

```

## Estimate carbon emissions from oil and gas volume

`oilgas_to_co2()` estimates CO2 emissions in tonnes for a given amount of oild and gas production in sm3. The conversion factors in here are currently very preliminary and need to be checked.

```{r}
sn17_co2 <- oilgas_to_co2(sn17)
sn17_co2

```


## Estimate carbon revenue from carbon emmission and carbon price

The function `get_revenue()` estimates the revenue from carbon emissions from carbon price. At present this uses an overly simple approach of multiplying the carbon price by the emissions, then reducing by 10% to account for reductions in carbon emissions (see Table 2 in [this](https://www.imf.org/external/np/g20/pdf/110411b.pdf) IMF report).

Here, we estimate revenue for a carbon price of $25 per metric tonne for the Senegal 2017 CO2 emissions estimate

```{r revenue}
get_revenue(25,sn17_co2)
```

## Get revenue directly for a given country and year

We can use the wrapper function `eiti_oilgas_revenue()` to estimate carbon pricing revenues directly for a given country and year, in millions of dollars

```{r wrapper}
eiti_oilgas_revenue("SN",2017,25)/1e06
```


## World bank data

```{r world_bank_read}
world_bank_raw <- read_csv('../../data-raw/world_bank_raw.csv',skip = 3)
```


```{r indicator_questions_template}

update_indicator_question_template('../../data-raw')

```

Fill in the template, then read back in to R

```{r indicators_questions}


indicator_survey_matrix<- read.csv('../../data-raw/indicators_survey_matrix.csv',row.names = 1,check.names = FALSE)
indicator_survey_matrix <- as.matrix(indicator_survey_matrix)
indicator_survey_matrix
```
```{r get indicators}

indicator_values <- get_wb_indicators(c(2010:2017),data_dir = '../../data-raw')
indicator_values
```
Plot an indicator

```{r plot indicator}

toplot <- filter(indicator_values,code == 'ST.INT.XPND.CD')

plot_indicator(toplot,10000000,2017)

```
