---
title: "Backend development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Read in EITI production data

The function `read_eiti_production()` reads in EIT production data from the API for a given country and year.

```{r read_eiti_production}
library(carpentr)

sn17 <- read_eiti_production("SN",2017)
sn17

```

## Estimate carbon emissions from oil and gas volume

`oilgas_to_co2()` estimates CO2 emissions in tonnes for a given amount of oild and gas production in sm3. The conversion factors in here are currently very preliminary and need to be checked.

```{r}
sn17_co2 <- oilgas_to_co2(sn17)
sn17_co2

```


## Estimate carbon revenue from carbon emmission and carbon price

The function `get_revenue()` estimates the revenue from carbon emissions from carbon price. At present this uses an overly simple approach of multiplying the carbon price by the emissions, then reducing by 10% to account for reductions in carbon emissions (see Table 2 in [this](https://www.imf.org/external/np/g20/pdf/110411b.pdf) IMF report).

Here, we estimate revenue for a carbon price of $35 per metric tonne for the Senegal 2017 CO2 emissions estimate

```{r revenue}
get_revenue(35,sn17_co2)
```

## Get revenue directly for a given country and year

We can use the wrapper function `eiti_oilgas_revenue()` to estimate carbon pricing revenues directly for a goven country and year

```{r wrapper}
eiti_oilgas_revenue("SN",2017,35)
```



